Personal Research and Articles

### 2024-05-09 articles.qmd
Update

## Is Public Housing Affordable for Singaporeans?
<p style="text-align: right;">  Monday, 6 Nov 2023 </p>

@@

<p style="text-align: right;">
    Photo Source: CNA
</p>
The findings emphasize the detrimental effects of punitive measures and highlight the need for supportive reintegration strategies. This case underscores the broader implications for educational policy and practices in managing deviance constructively.

### Background
![](docs/src/images/soon.avif){width="730"}

>>>>

## Is Public Housing Affordable for Singaporeans?

<p style="text-align: right;"> Monday, 6 Nov 2023 </p>

@@

<p style="text-align: right;"> Photo Source: CNA </p>

The findings emphasize the detrimental effects of punitive measures and highlight the need for supportive reintegration strategies. This case underscores the broader implications for educational policy and practices in managing deviance constructively.

### Background

<p> In the heart of Singapore's rigorous educational landscape, shaped by the Compulsory Education Act of 2000, every child is promised a solid 10-year foundational education. But beneath these statistics lies the personal struggle of students like Jeremy, whose life challenges disrupt the ideal path set before them.

### The Story of Jeremy

![](docs/src/images/study.png)

<p> "School was my second home until it wasn't," Jeremy recalls, his journey from a model student to a labeled 'truant' marked by circumstances beyond his control. When his father fell ill, the burden of financial support fell on his shoulders, forcing him to balance part-time jobs with his studies. This new responsibility led to tardiness and eventually, absences, which didn't go unnoticed. "I wasn't just late; I was struggling to keep my life together," Jeremy shares.</p>

### The Spiral of Deviance

<p> Jeremy's initial minor infractions soon snowballed into more significant absences. "Each late coming wasn't just about not making it on time; it was about not making it at all," Jeremy explains. The school's response was punitive---detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant. "You're marked, and that marking changes how everyone sees you," he reflects.</p>

### Labeling and Its Impacts

<p> The transformation in how Jeremy was perceived and treated is a classic example of labeling theory in action. "Once labeled, you're playing a part scripted for you by those labels," Jeremy says. This script was reinforced continually by the detentions and the reactions of his teachers and peers. "When you hear 'Wah, bro finally showed up?' enough times, you start to wonder if trying is worth it," he admits.

### Breaking Free

<p> The turning point came with the passing of his father. This profound loss forced Jeremy to reassess his life's direction. "It made me realize the shortness of life and the long-term consequences of my choices," he states. Motivated by his father's memory and the need to support his family, Jeremy began to shed his truant identity. "I was more than my circumstances," he asserts.</p>

### Insights from Educators

<p> Educators like Mrs. Tan, Jeremy's guidance counselor, emphasize the importance of understanding each student's context. "We need to look beyond the behavior to the person behind it. Only then can we truly help," she notes. Mrs. Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around."</p>

### Conclusion

<p> Jeremy's narrative is a reminder of the complexity of deviance within Singapore's educational system. His experiences underscore the critical need for educational policies that foster understanding and provide genuine support. As Jeremy continues his journey, now a student at a university in Singapore, his story offers hope and a call to action for all involved in shaping young lives. "Change starts when we choose to see the person, not just the problem," Jeremy concludes.</p>
